%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Stelios}{Daveas}{ \urlstyle{same}
\href{mailto:sdaveas@gmail.com}{sdaveas@gmail.com} | +30 697 913 9967 |
\href{https://www.github.com/sdaevas}{github.com/sdaveas} }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of Athens}
\descript{M.S in Computer Science}
\location{2017-2019 | Athens, GR}
\sectionsep

\subsection{University of Athens}
\descript{B.S in Computer Science}
\location{2010-2016 | Athens, GR}
\sectionsep
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
C/C++ \textbullet{}
Python \textbullet{}
Rust \textbullet{}
Golang \textbullet{}
Solidity \textbullet{}
Java \textbullet{}
LUA \textbullet{}
Bash \textbullet{}
\LaTeX\ \textbullet{}
Matlab \\
\sectionsep

\subsection{Concepts}
Blockchain \textbullet{}
gRPC \textbullet{}
AWS \textbullet{}
Protobufs \textbullet{}
Smart Contracts \textbullet{}
OOP \textbullet{}
Test driven development \textbullet{}
Data-Oriented Programming \textbullet{}
Parallel Programming \textbullet{}
Network Programming
\sectionsep

\subsection{Environments}
Mac \textbullet{}
Linux \textbullet{}
Git \textbullet{}
Vim \textbullet{}
Tmux
\sectionsep

\subsection{Infrastructure}
Docker \textbullet{}
Kubernates \textbullet{}
Docker \textbullet{}
Terraform
\sectionsep

\subsection{Databases}
PostgreSQL \textbullet{}
MySQL \textbullet{}
MariaDB \\
MongoDB \\
\sectionsep

\subsection{Languages}
English \textbullet{}
German \textbullet{}
Greek (\textbf{native})

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\runsubsection{Axelar}
\descript{| Software Engineer }
\location{2020 – present | remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \textbf{Head engineer} at an \textbf{open source} gRPC threshold signature scheme daemon in \textbf{Rust} (\textit{\href{https://github.com/axelarnetwork/tofnd}{tofnd}}).
\item Software engineer at an \textbf{open source} threshold cryptography library in \textbf{Rust}. (\textit{\href{https://github.com/axelarnetwork/tofn}{tofn}}).
\item Contributed \textbf{45K LOC} -- no vulnerabilities found through multiple audits.
\item Software engineer building microservices on \textbf{AWS} around blockchains in \textbf{Golang}.
\item Worked with the \textbf{Cosmos SDK} to build services for the \textbf{Axelar} blockchain.
\item Infrastructure building using \textbf{kubernates}, \textbf{docker} and \textbf{terraform}.
\item One-click deployments with \textbf{Github actions}.
\item Design of system architecture.
\item \textbf{Code reviews} at GitHub.
\item Cooperation with a \textbf{20-member team} in daily basis.
\end {tightemize}
\sectionsep


\runsubsection{University of Athens}
\descript{| Software Engineer }
\location{2019 – 2020 | Athens, GR}
\begin{tightemize}
\item Implementation of gas-efficient smart contracts in \textbf{Solidity},
    profiling and auditing.
\item Implementation of development and testing environment for smart contracts
    in \textbf{Python} using
    \textbf{\href{https://web3py.readthedocs.io/en/stable/}{Web3}} interface.
\item \textbf{Test driven} development.
\item Daily stand-ups using \textbf{Slack}.
\end {tightemize}
\sectionsep

\runsubsection{NCSR Demokritos}
\descript{| Software Engineer }
\location{2016 – 2020 | Athens, GR}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item \textbf{Head engineer} at \textbf{\href{https://ui.adsabs.harvard.edu/abs/2016SPIE.9842E..0QK/abstract}{in-house simulation engine}}, used in \textbf{5+ H2020 European projects}.
\item Advanced status from TRL 5 to \textbf{TRL 7}, contributed \textbf{48K LOC} of
    high-performance code at a 300K LOC codebase, performed maintenance,
    migrated from
C++03 to \textbf{C++17} standards.
\item \textbf{Code review} on GitLab.
\item Incorporated open source projects \textbf{\href{https://github.com/ocornut/imgui}{ImGui}} and \textbf{\href{https://github.com/recastnavigation/recastnavigation}{Recast}}.
\item \textbf{LUA} scripting and implementation of bindings for C++.
\item Design of system architecture.
\item Communication with \textbf{end users} to define requirements.
\item Conducted \textbf{interviews}.
\item Build \textbf{containerized} services.
\item Administration of Linux servers.
\end {tightemize}
\sectionsep


% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     RESEARCH
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Research}
% \runsubsection{University of Athens}
% \descript{| Postgraduate Student}
% \location{2020 | Athens, GR}
% Worked with
% \textbf{Kostis Karantias},
% \textbf{Prof. Aggelos Kiayias} and \textbf{Dr. Dionysis Zindros} to create the
% first gas-efficient superlight client smart contract based on the
% \href{https://www.nipopows.com}{NIPoPoW} protocol.

% \runsubsection{NCSR Demokritos}
% \descript{| Researcher}
% \location{2019 | Athens, GR}
% Worked with
% \textbf{Giorgos Bouritsas},
% \textbf{Dr. Antonios Danelakis} and \textbf{Dr. Stelios Thomopoulos} to create
% and architecture that leverages the detection of anomalous human trajectories
% using a Sequence-to-Sequence architecture.
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}

\underline{Daveas S.}, Karantias K., Kiayias A. \& Zindros D.: \href{https://dl.acm.org/doi/abs/10.1145/3419614.3423255?casa_token=NmylSoSMSJgAAAAA:yOyuE4bgCLLp8HQP0MHzGegNr6IVBofjx77nBAiDxN6WzWIzarMpyMD14UMf5Wki-guZkenxekT2qw}{\textbf{A Gas-Efficient
Superlight Bitcoin Client in Solidity}, ACM AFT 2020}

Bouritsas G., \underline{Daveas S.} Danelakis A. and Thomopoulos S.:
\href{https://ieeexplore.ieee.org/abstract/document/8909844/?casa_token=NlZHO6W9_ewAAAAA:2Q2vSiR0ynu72R9iaYASHe5FzuNVAtfDrmnj0VmEk1sBZ-P74vnzKELd71hpL59byzko7acsjf5Nlw}{\textbf{
Automated Real-time Anomaly Detection in Human Trajectories using Sequence to
Sequence Networks}},
IEEE AVSS 2019
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
